Make any stupid plot you want

### 2021-01-26 draft/sections/math.tex
artist _ fiber _nu

\subsection{Artist}
\label{sec:artist}
The artist is the composite function that converts data into graphics; its name is taken from the analogous part of the existing Matplotlib architecture. The binding of $\xi:S \rightarrow K$ keeps track of which data goes to which part of the graphic such that the artist can be trivially parallelized or formulated as a delayed computer graph or otherwise not need to immediately work on all the data.

The artist is a mapping from $E$ padded with data from $\mathcal{J}(E)$
\begin{equation}
    A: E^\prime \rightarrow \Gamma(H)
\end{equation}
\note{this is soup}
to a graphic in $\Gamma(H)$. The artist decomposes to mapping data to visual $\nu:E\rightarrow V$, then  compositing $V$ pulled back along $\xi$ to $\xi^*V$ to a visual mark in prerender space $Q:\xi^*V\rightarrow H$.

\begin{equation}
    \label{eq:artist_diagram}
    \begin{tikzcd}
        E \arrow[r, "\nu"] \arrow[rd, "\pi"'] & V \arrow[d, "\pi"] & \xi^*V \arrow[r, "Q"] \arrow[d, "\xi^*\pi"'] \arrow[l, "\xi^*"'] & H \arrow[ld, "\pi"] \\
                                              & K                  & S \arrow[l, "\xi"']                                              &                    
        \end{tikzcd}
\end{equation}
The pullback map $\xi^*$ copies each value in $V$ over $k$ to $s$ in corresponding $S_k$ such that $\xi^*V$ can have multiple values that map to one value in $V$.

The visual fiber bundle ($V$, $K$, $\pi$, $P$) has section $\mu: V \rightarrow K$ that resolves to a visual variable \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels,} in fiber $P$.
\begin{figure}
    \includegraphics[width=\textwidth]{figures/math/artist_stages.png}
    \caption{The artist $A$ converts data into the visual variables in $V$ and then composes those visual variables into a graphic in $H$}
    \label{fig:artist_stages}
\end{figure}
\subsubsection {Visual Fiber Bundle}

For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{codomain(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^{4}$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $\{f_{0}, \ldots, f_{n}\} \times (\mathbb{R}, \mathbb{R^+}^{n, n\%2=0})$ \\ \hline              
    \end{tabulary}
    \label{tab:mpl_visual_variable_fiber}
\end{table}

Table~\ref{tab:mpl_visual_variable_fiber} is an example of the visual fiber defined in terms of common parameters to plots in Matplotlib. The range of $\mu_{i}$ determine the monoid actions on $\mu_{i}$. A section of V $\mu$ is a tuple of visual values that specifies the visual characteristics of a glyph. For example, given a fiber of $\{xpos, ypos, color\}$ one section is $\{.5, .5, (255, 20,147)\}$. $Q$ determines how this section is applied to a graphic.

@@

\subsubsection{Assembling Marks}
\label{sec:artist_q}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/path_of_q}
    \label{fig:artist_q}
    \caption{The $\nu$ functions convert data $E$ to visual $V$. $Q$ assembles the different types of visual parameters $V_{i}$ into a graphic in $H$. $Q\circ\mu(\xi^{-1}J)$ forms a visual mark by applying $Q$ to a region mapped to connected components $J \subset K$.}
    %%maybe change to \tau, \mu, \rho  
\end{figure}

@@

\subsection{Making the fiber bundle computable}
\label{sec:triangulization}

@@

\subsubsection{Visual Idioms: Equivalance class of artists}
As formulated above, every artist function $A$ has fixed $\nu$ and generates a distinct graphic $\rho$. It is unfeasible to implement $A$ for every single graphic; instead we implement the equivalence class of artists $\{A \in A^\prime: A_{1} \equiv A_{2}\}$ which is $Q:\Gamma(V) \rightarrow \Gamma(H)$.

>>>>

\subsection{Artist}
\label{sec:artist}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/dar.png}
    \caption{The artist $A$ converts an section of data $\tau$ into a section of visual equivalents $\mu$ that are then composed into a piece of a glyph defined by the graphic section $\rho$
    \note{might need to label this as E', V, H}}
    \label{fig:artist_stages}
\end{figure}

The artist is the function that converts data into graphics; its name is taken from the analogous part of the existing Matplotlib architecture that builds visual elements to pass off to the renderer. The artist is a mapping from $E$ padded with data from $\mathcal{J}(E)$ to a graphic that is a section $\rho$ in  $\Gamma(H)$
\begin{equation}
    \label{eq:artist_diagram}
    \begin{tikzcd}
        E' \arrow[r, "\nu"] \arrow[rd, "\pi"'] & V \arrow[d, "\pi"] & \xi^*V \arrow[r, "Q"] \arrow[d, "\xi^*\pi"'] \arrow[l, "\xi^*"'] & \Gamma(H) \arrow[ld, "\pi"] \\
                                              & K                  & S \arrow[l, "\xi"']                                              &                    
        \end{tikzcd}
\end{equation}
with an intermediate fiber bundle $V$ to hold visual representations and stages
\begin{enumerate}
    \item $\xi$ binding the continuity in the graphic to the continuity in the data (~\ref{sec:graphic_base})
    \item $\nu$ conversion of data into visual characteristics (~\ref{sec:artist_nu})
    \item $Q$ assembly of visual variables into a glyph (~\ref{sec:artist_q})
\end{enumerate}

of the visual transformation illustrated in figure~\ref{fig:artist_stages}. The functions $\xi$, $\nu$ and $Q$ are constructed such that the input can be a single section on $K$ or $S$, which allows the artist to be trivially parallelized or formulated as a delayed computer graph or otherwise not need to immediately work on all the data.

\subsubsection {Visual Fiber Bundle $V$}
The visual fiber bundle ($V$, $K$, $\pi$, $P$) has section $\mu: V \rightarrow K$ that resolves to a visual variable \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels,} in fiber $P$. The fiber space $P$ is defined in terms of the parameters of the visualization specification and the values those parameters resolve to - for example APT\cite{mackinlayAutomatingDesignGraphical1986} or Vega\cite{satyanarayanDeclarativeInteractionDesign2014}.

\begin{table}[H]
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{codomain(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^{4}$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $\{f_{0}, \ldots, f_{n}\} \times (\mathbb{R}, \mathbb{R^+}^{n, n\%2=0})$ \\ \hline              
    \end{tabulary}
    \caption{Some possible components of the fiber $P$ for a visualization implemented in Matplotlib}
    \label{tab:mpl_visual_variable_fiber}
\end{table}

Table~\ref{tab:mpl_visual_variable_fiber} is a sample of the fiber space for Matplotlib \cite{hunterMatplotlib2DGraphics2007}.  
A section $\mu$ of $V$ is a tuple of visual values that specifies the visual characteristics of a part of the graphic. For example, given a fiber of $\{xpos, ypos, color\}$ one possible section could be  $\{.5, .5, (255, 20,147)\}$. The $codomain(\nu_i)$ determines the monoid actions on $\mu_i)$. These fiber components are implicit in the library, by making them explicit as components of the fiber we can build consistent definitions and expectations of how these parameters behave.

@@

\subsubsection{Assembling Marks}
\note{HAVE NOT REACHED HERE TO EDIT YET}
\label{sec:artist_q}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/path_of_q}
    \label{fig:artist_q}
    \caption{The $\nu$ functions convert data $E$ to visual $V$. $Q$ assembles the different types of visual parameters $V_{i}$ into a graphic in $H$. $Q\circ\mu(\xi^{-1}J)$ forms a visual mark by applying $Q$ to a region mapped to connected components $J \subset K$.}
    %%maybe change to \tau, \mu, \rho  
\end{figure}

@@

\subsection{Making the fiber bundle computable}
\label{sec:triangulization}
\note{HAVE NOT REACHED HERE TO EDIT YET}

@@

\subsubsection{Visual Idioms: Equivalance class of artists}
\note{HAVE NOT REACHED HERE TO EDIT YET}
As formulated above, every artist function $A$ has fixed $\nu$ and generates a distinct graphic $\rho$. It is unfeasible to implement $A$ for every single graphic; instead we implement the equivalence class of artists $\{A \in A^\prime: A_{1} \equiv A_{2}\}$ which is $Q:\Gamma(V) \rightarrow \Gamma(H)$.
